From Reversible Programs to \\ Univalent Universes and Back

### 2021-05-24 Pi+/paper/finite.tex
Add notes and comments

In this section, we describe the algebraic structure of the groupoid of finite
types, and give a computable presentation for it. To do so, we will characterise
the automorphisms on finite sets of cardinality $n$, and show them to be
equivalent to the symmetric group $\Sn$, via the Coxeter presentation. We will
do that in two steps,
in~\cref*{subsec:permutations,subsec:lehmer,subsec:symmetric}.

@@

\begin{definition}
  \begin{align*}
    I           & \defeq \Fin[0]    \\
    X \otimes Y & \defeq X \sqcup Y
  \end{align*}
\end{definition}

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:

>>>>

In this section, we describe \review{the algebraic structure} of the groupoid of
finite types, and give \review{a computable presentation} for it.

\vc{The groupoid of finite types is the free symmetric monoidal groupoid on one
  generator. This can be presented as an algebraic 2-theory, which is our syntax
  for $\PiHatLang$. Vertical categorification of natural numbers as a free
  commutative monoid. See groupoidification.}

\todo{Check Brent Yorgey's thesis?}

To do so, we will characterise the automorphisms on finite sets of cardinality
$n$, and show them to be equivalent to the symmetric group $\Sn$, via the
Coxeter presentation. We will do that in two steps,
in~\cref*{subsec:permutations,subsec:lehmer,subsec:symmetric}.

@@

\begin{definition}
  \begin{align*}
    I           & \defeq F_{0}    \\
    X \otimes Y & \defeq X \sqcup Y
  \end{align*}
\end{definition}

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% fill-column: 120
%%% End:
